

\section{PDF Recreation in Latex}

\subsection{Objective}
The task was to create a LaTeX document formatted to replicate the provided example. The final submission required the following components:
\begin{itemize}
    \item Source code (\texttt{.tex})
    \item Output document in PDF format (\texttt{.pdf})
    \item An image file (\texttt{.png} or \texttt{.jpg})
\end{itemize}
These files were to be zipped and named according to the format: 

\texttt{Rollno\_DeptName\_Firstname.zip}.

\subsection{Steps Taken}

\subsubsection{1. Document Setup}
The LaTeX document was structured to match the provided template, including sections such as:
\begin{itemize}
    \item Introduction with subsections on personal background and interests.
    \item A section for favorite quotations.
    \item A mathematics section, detailing mathematical expressions, tables, and formulas.
\end{itemize}

\subsubsection{2. Mathematical Typesetting}
Mathematical notation was included as per the requirements:
\begin{itemize}
    \item Superscripts, subscripts, and Greek letters.
    \item Fractions, roots, and complex display math.
    \item Tables and equation arrays were implemented, adhering to the provided mathematical structures.
\end{itemize}

\subsubsection{3. Image Inclusion}
A placeholder for an image was added in the document, simulating the space for a profile photo. An image was uploaded in the required \texttt{.png} or \texttt{.jpg} format, to ensure full compliance with the task requirements.

\subsubsection{4. Output Generation}
The source code (\texttt{.tex}) was compiled to generate the final output document in PDF format (\texttt{.pdf}). The files were verified to ensure that the output matched the provided format.

\subsubsection{5. Final Packaging}
The source code, PDF output, and image files were compressed into a single zip file following the naming convention: \texttt{Rollno\_DeptName\_Firstname.zip}.

\subsection{Conclusion}
The LaTeX document was successfully created and compiled in accordance with the provided instructions. The output matched the formatting and structural requirements of the example, and the necessary files were packaged and submitted as per the guidelines.

